A Comparison of Graph Processing Systems

### 2020-09-21 documentation/paper/main.tex
merge und besprechung

\section{Evaluation}
The main part of this paper is the evaluation, which consists of two parts. The first is a description and explanation of our testing environment and methodology. Followed by a lengthy presentation and discussion of the test results of the frameworks.

@@

\section{Discussion}
\todo{Hier zunächst mal ein kurzer Vergleich zwischen Distributed und Single Node wo sinnvoll, dann zwischen den Frameworks und so weiter..}

>>>>

\section{Evaluation}
The main part of this paper is the evaluation, which consists of two parts. The first is a description and explanation of our testing environment and methodology. Followed by a presentation and discussion of the test results of the frameworks.

@@

\input{sections/discussion}

### 2020-09-21 documentation/paper/sections/results/results.tex
merge und besprechung

\subsubsection{Lessons Learned}

\todo{umbenennen?}

We would like to raise some issues we encountered first while installing and configuring and second while running the different frameworks.

@@

\subsubsection{Comparison of a Single-Node to the Distributed Cluster}
\begin{table}
	\caption{Execution Times in Seconds on a SingleNode vs. 5-Node Distributed Cluster}
	\label{tbl:execTimeComparison}
	\renewcommand{\arraystretch}{1.2}
	\centering
	\begin{tabular}{ccr@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r}
		\toprule
		&&\multicolumn{2}{c}{\bf Galois}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
		\cmidrule{3-4}\cmidrule{5-6}\cmidrule{7-8}
		&\bf Graph&1N&5N&1N&5N&1N&5N\\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}&flickr & 0.3 & 2.4 & 0.6 & 2.5 & 38.8 & 42.6 \\
		& orkut & 0.8 & 4.2 & 13.9 & 17.3 & 135.9 & 60.4 \\
		& wikipedia & 1.8 & 14.2 & 48.5 & 74.5 & 377.2 & 100.8 \\
		& twitter & 10.8 & 40.0 & 383.0 & 391.1 & - & 349.9 \\
		& rMat27 & 16.0 & 39.0 & 563.5 & 386.0 & - & 565.8 \\
		& friendster & 14.4 & 58.5 & 742.6 & 568.9 & - & 444.0 \\
		& rMat28 & 27.8 & 71.5 & 1236.7 & 792.0 & - & 1180.2 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf BFS}}& flickr & 0.6 & 2.3 & 0.7 & 2.4 & 38.9 & 41.9 \\
		& orkut & 0.9 & 4.0 & 12.5 & 13.8 & 128.2 & 58.1 \\
		& wikipedia & 2.4 & 13.2 & 44.9 & 60.9 & 360.7 & 95.1 \\
		& twitter & 14.2 & 37.9 & 355.0 & 293.2 & - & 322.3 \\
		& rMat27 & 14.6 & 34.4 & 540.8 & 305.3 & - & 539.2 \\
		& friendster & 12.8 & 47.6 & 708.4 & 450.2 & - & 412.3 \\
		& rMat28 & 33.1 & 67.1 & 1178.7 & 634.3 & - & 1135.6 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR}}& flickr & 0.3\txtdagger & 2.6 & 0.7 & 2.2 & 45.6 & 44.1 \\
		& orkut & 0.7\txtdagger & 8.0 & 13.1 & 19.4 & 561.3 & 106.2 \\
		& wikipedia & 1.7\txtdagger & 206.5 & 44.4 & 54.4 & 1501.3 & 252.6 \\
		& twitter & 8.7\txtdagger & 910.9 & 359.9 & 363.5 & - & 1200.2 \\
		& rMat27 & 19.2\txtdagger & 1287.4 & 536.3 & 376.3 & - & 1369.5 \\
		& friendster & 20.4\txtdagger & 593.3 & 716.5 & 591.1 & - & 1655.0 \\
		& rMat28 & 46.0\txtdagger & 2540.2 & 1188.5 & 774.2 & - & - \\
		\bottomrule
		\multicolumn{8}{l}{(\txtdagger) Results of Galois Pull shown.}
	\end{tabular}
\end{table}
Until now, we have only compared the frameworks with each other, under the same setup circumstances. Hence, a comparison of the same framework, in single-node versus distributed setup is the content of this section.
Of course only frameworks that were tested in both setups are shown.
We focus primarily on the results of the execution times, the data can be seen in \autoref{tbl:execTimeComparison}. We show the results of Galois Push for the 5-node cluster in the table, since it is faster than Pull.

>>>>

\subsubsection{Encountered Issues}
We would like to raise some issues we encountered first while installing and configuring and second while running the different frameworks.

@@

\subsubsection{Comparison of a Single-Node to the Distributed Cluster}
\begin{table}
	\caption{Execution Times in Seconds on a Single Node vs. 5-Node Distributed Cluster}
	\label{tbl:execTimeComparison}
	\renewcommand{\arraystretch}{1.2}
	\centering
	\begin{tabular}{ccr@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r
	r@{\tabskip 1 \tabcolsep}r}
		\toprule
		&&\multicolumn{2}{c}{\bf Galois}&\multicolumn{2}{c}{\bf Gemini}&\multicolumn{2}{c}{\bf Giraph}\\
		\cmidrule{3-4}\cmidrule{5-6}\cmidrule{7-8}
		&\bf Graph&1N&5N&1N&5N&1N&5N\\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}&flickr & \bf 0.3 & 2.4 & \bf 0.6 & 2.5 & \bf 38.8 & 42.6 \\
		& orkut & \bf 0.8 & 4.2 & \bf 13.9 & 17.3 & 135.9 & \bf 60.4 \\
		& wikipedia & \bf 1.8 & 14.2 & \bf 48.5 & 74.5 & 377.2 & \bf 100.8 \\
		& twitter & \bf 10.8 & 40.0 & \bf 383.0 & 391.1 & - & \bf 349.9 \\
		& rMat27 & \bf 16.0 & 39.0 & 563.5 & \bf 386.0 & - & \bf 565.8 \\
		& friendster & \bf 14.4 & 58.5 & 742.6 & \bf 568.9 & - & \bf 444.0 \\
		& rMat28 & \bf 27.8 & 71.5 & 1236.7 & \bf 792.0 & - & \bf 1180.2 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf BFS}}& flickr & \bf 0.6 & 2.3 & \bf 0.7 & 2.4 & \bf 38.9 & 41.9 \\
		& orkut & \bf 0.9 & 4.0 & \bf 12.5 & 13.8 & 128.2 & \bf 58.1 \\
		& wikipedia & \bf 2.4 & 13.2 & \bf 44.9 & 60.9 & 360.7 & \bf 95.1 \\
		& twitter & \bf 14.2 & 37.9 & 355.0 & \bf 293.2 & - & \bf 322.3 \\
		& rMat27 & \bf 14.6 & 34.4 & 540.8 & \bf 305.3 & - & \bf 539.2 \\
		& friendster & \bf 12.8 & 47.6 & 708.4 & \bf 450.2 & - & \bf 412.3 \\
		& rMat28 & \bf 33.1 & 67.1 & 1178.7 & \bf 634.3 & - & \bf 1135.6 \\
		\midrule
		\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR}}& flickr & \bf 0.3\txtdagger & 2.6 & \bf 0.7 & 2.2 & 45.6 & \bf 44.1 \\
		& orkut & \bf 0.7\txtdagger & 8.0 & \bf 13.1 & 19.4 & 561.3 & \bf 106.2 \\
		& wikipedia & \bf 1.7\txtdagger & 206.5 & \bf 44.4 & 54.4 & 1501.3 & \bf 252.6 \\
		& twitter & \bf 8.7\txtdagger & 910.9 & \bf 359.9 & 363.5 & - & \bf 1200.2 \\
		& rMat27 & \bf 19.2\txtdagger & 1287.4 & 536.3 & \bf 376.3 & - & \bf 1369.5 \\
		& friendster & \bf 20.4\txtdagger & 593.3 & 716.5 & \bf 591.1 & - & \bf 1655.0 \\
		& rMat28 & \bf 46.0\txtdagger & 2540.2 & 1188.5 & \bf 774.2 & - & - \\
		\bottomrule
		\multicolumn{8}{l}{(\txtdagger) Results of Galois Pull shown.}
	\end{tabular}
\end{table}
Until now, we have only compared the frameworks with each other, under the same setup circumstances. Hence, a comparison of the same framework, in single-node versus distributed setup is the content of this section.
Of course only frameworks that were tested in both setups are shown.
We focus primarily on the results of the execution times, the data can be seen in \autoref{tbl:execTimeComparison}. We show the results of Galois Push for the 5-node cluster in the table, since it is faster than Pull.

### 2020-09-21 documentation/paper/sections/testingMethods.tex
merge und besprechung

\subsection{Testing Methods}
\todo{Einleitung}

@@

In detail, the algorithms for each framework are:
\todo{Algorithmen auflisten}
\begin{itemize}
	\item Ligra supports SSSP based on BellmanFord, BFS and two implementations of PageRank. The two implementations are a regular PR and a Delata Variant.
	\item Polymer supports the same algoritms as ligra.
	\item Gemini supports all of our tested algorithms and there are no setting options or specifications which implementations for the algorithms are used.
	\item Galois supports all of our tested algorithms too, with both a Push and a Pull variant for PageRank available. In the distributed scenario, there are Push and Pull versions for SSSP and BFS available as well. It also supports multiple implementations of the shared-memory allgorithms. The default implementation of SSSP is deltaTile. A lot of setting options are avilable as well, but we're gone with the defaults.
	\item Giraph does not natively supply a BFS algorithm, so in our comparisons a custom implementation is used. For SSSP, slight variations had to be made to the default implementation, to allow us to use different start vertices. For PageRank the supplied implementation is used.
\end{itemize}

>>>>

\subsection{Testing Methods}
The testing methods cover the test environment, including hardware and the setup of the frameworks, the graphs used, followed by the algorithms utilized and how the times are measured.

@@

In detail, the algorithms for each framework are:
\begin{itemize}
	\item Ligra supports SSSP based on BellmanFord, BFS and two implementations of PageRank. The two implementations are a regular PR and a Delta Variant.
	\item Polymer supports the same algoritms as Ligra.
	\item Gemini supports all of our tested algorithms and there are no setting options or specifications which implementations for the algorithms are used.
	\item Galois supports all of our tested algorithms too, with both a Push and a Pull variant for PageRank available. In the distributed scenario, there are Push and Pull versions for SSSP and BFS available as well. It also supports multiple implementations of the shared-memory allgorithms. The default implementation of SSSP is deltaTile. A lot of setting options are avilable as well, but we're gone with the defaults.
	\item Giraph does not natively supply a BFS algorithm, so in our comparisons a custom implementation is used. For SSSP, slight variations had to be made to the default implementation, to allow us to use different start vertices. For PageRank the supplied implementation is used.
\end{itemize}
